sWGS validation report

### 2019-09-06 Validation Report.Rmd
Rank adjust validation?

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf'
preds.dir = paste0(analysis.dir, '/predictions/fourier')

@@

ggplot(new.np.preds, aes(`Hospital Research ID`, Probability, color=Probability)) + geom_point(size=2) +
  scale_color_distiller(palette = 'RdYlBu', name='P(P)') + plot.theme + theme(axis.text.x = element_text(angle=45,hjust=1))
```

@@

roc = pROC::roc(Status ~ Probability, data = all, auc=T, ci=T, of='thresholds',transpose=T)
roc.plot(roc)
#pROC::coords(roc, 'best', transpose=T)
```

>>>>

val.file = '~/Data/BarrettsProgressionRisk/QDNAseq/validation/sWGS_validation_batches.xlsx'
analysis.dir = '~/Data/BarrettsProgressionRisk/Analysis/validation/multipcf'
preds.dir = paste0(analysis.dir, '/predictions/0.9')

@@

ggplot(new.np.preds, aes(`Hospital Research ID`, Probability, color=Probability)) + geom_point(size=2) +
  scale_color_distiller(palette = 'RdYlBu', name='P(P)') + plot.theme + theme(axis.text.x = element_text(angle=45,hjust=1))

ggplot(new.np.preds, aes(`Hospital Research ID`, `Relative Risk`, color=Probability)) + geom_point(size=2) +
  scale_color_distiller(palette = 'RdYlBu', name='RR') + plot.theme + theme(axis.text.x = element_text(angle=45,hjust=1))

@@

roc = pROC::roc(Status ~ Probability, data = all, auc=T, ci=T, of='thresholds',transpose=T)
roc.plot(roc)
#pROC::coords(roc, 'best', transpose=T)

ggplot(all, aes(Status, `Relative Risk`, color=`Relative Risk`, group=Status)) + geom_boxplot() + geom_jitter(width=0.1)
